Solar jet observed at the limb in SDO/SST

### 2016-07-28 paper/ms_temp_paper.tex
begininng of description of dops

\begin{pycode}[doppler]
import sunpy
from sunpy.image import slit

@@

path_dop_1 = manager.data_file('dops/dop_arr_test075.npy')
path_dop_2 = manager.data_file('dops/dop_arr_test076.npy')
path_dop_3 = manager.data_file('dops/dop_arr_test077.npy')
path_dop_4 = manager.data_file('dops/dop_arr_test078.npy')
path_dop_5 = manager.data_file('dops/dop_arr_test079.npy')
path_dop_6 = manager.data_file('dops/dop_arr_test080.npy')
path_dop_7 = manager.data_file('dops/dop_arr_test081.npy')
path_dop_8 = manager.data_file('dops/dop_arr_test082.npy')
path_dop_9 = manager.data_file('dops/dop_arr_test083.npy')
path_dop_10 = manager.data_file('dops/dop_arr_test084.npy')
path_dop_11 = manager.data_file('dops/dop_arr_test085.npy')
path_dop_12 = manager.data_file('dops/dop_arr_test086.npy')
path_dop_13 = manager.data_file('dops/dop_arr_test087.npy')
path_dop_14 = manager.data_file('dops/dop_arr_test088.npy')
path_dop_15 = manager.data_file('dops/dop_arr_test089.npy')
path_dop_16 = manager.data_file('dops/dop_arr_test090.npy')

@@

dop_gird.placement = 't'
dop_grid.caption = 'Captiony things'

@@

>>>>

\begin{pycode}[DOPPLER]
import sunpy
from sunpy.image import slit

@@

@@

dop_gird.placement = 't'
dop_grid.caption = ''

@@

\py[DOPPLER]|dop_grid|

The dopplergrams demonstrated in \cref{fig:dop_grid}
Applying the method described above, we obtain dopplergrams of the feature when applied to the spectroscopic data produced by CRISP, presented in \cref{fig:dop_grid}.
The immediately apparent when we examine the data is the difficulty in clearly identifying the jet, with the complex background demonstrating shifts in both directions.
This is due top the effect of observing along the limb, we see features further round the disk as bulk motions.
The jet we are examining, apparently originates in a 'bank' of spicules, visible as lines of red shift in the image.
The initial acceleration of the spicule at $07:30$ shows no rotational motion and is infact hard to differentiate from the background.
However, the second jet formation and consequent acceleration reveal significant rotational motion.

As the onset occurs we first observe blue shifting on the right side of the jet
